Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-09-13 ms.tex
version that was actually submitted

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
matches the dust spectrum near its peak, accounts for the flattening of the 
dust spectrum at millimeter wavelengths, and specifies dust temperature at 
6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
regions, our two-component 100-217 GHz thermal dust emission predictions are on
average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
at visible wavelengths, and compare the resulting reddening estimates with 
those based on stellar spectra. We find imperfect zodiacal light subtraction in
both DIRBE/\IRAS~and \PLANCK~to be the dominant large angular scale systematic 
problem in our two-component temperature map and reddening estimates.

>>>>

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to \PLANCK~217-857 GHz along 
with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
matches the dust spectrum near its peak, accounts for the flattening of the 
dust spectrum at millimeter wavelengths, and specifies dust temperature at 
6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
foreground predictions from 100 to 3000 GHz. We find that, in diffuse sky 
regions, our two-component 100-217 GHz predictions are on
average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
and 7.9\% at 217 GHz. We calibrate our two-component optical depth to 
reddening, and compare the resulting reddening estimates with 
those based on stellar spectra. We find imperfect zodiacal light subtraction in
both DIRBE/\IRAS~and \PLANCK~to be the dominant large angular scale systematic 
problem in our two-component temperature map and reddening estimates.
